Competing Bandits: \\ The Perils of Exploration under Competition

### 2019-02-14 paper/content/conclusion.tex
Revised conclusions.

\gaedit{In this paper we considered a setting where firms simultaneously learn from and compete for users. We showed that competition may not always induce firms to commit to algorithms that engage in exploration resulting in welfare losses for consumers. The primary mechanism behind this was that exploration may have short-term reputational consequences that lead to naive algorithms winning in competition that are bad in the long-run. Allowing one firm to have a head start, or a first-mover advantage, leads to the first-mover having an incentive to play traditionally ``good" bandit algorithms and resulting in significantly better welfare for consumers. Finally, we attempted to isolate the effect that the data advantage of an incumbent has on its ability to garner a considerable market share. Contrary to previous studies and discussions which do not consider competition dynamics, we find that the data advantage is substantial in generating significant market power. Additionally we show that this effect is strongest when an incumbent \swedit{performs efficient exploration in the incumbency period without the pressure from a competitor.}}

>>>>

\asedit{We consider a stylized duopoly setting where firms simultaneously learn from and compete for users. We showed that competition may not always induce firms to commit to better exploration algorithms, resulting in welfare losses for consumers. The primary reason is that exploration may have short-term reputational consequences that lead to more naive algorithms winning in a long-term competition. Allowing one firm to have a head start, a.k.a. the first-mover advantage, incentivizes the first-mover to deploy ``better" algorithms, which in turn leads to better welfare for consumers. Finally, we isolate the component of the first-mover advantage that is due to having more initial data, and find that even a small amount of this ``data advantage" leads to substantial long-term market power.}
